Functional Pearl: Short and Mechanized Logical Relation for Dependent Type Theories

### 2024-12-03 paper/paper.tex
Supress an orphan

The next lemma shows that the logical relation is cumulative:
if a type has an interpretation at a lower universe level,
then we can obtain the same interpretation at a higher universe level.

>>>>

The next lemma shows cumulativity of the logical relation:
if a type has an interpretation at a lower universe level,
then we obtain the same interpretation at a higher level.
